A meta-analysis of mental rotation ability in the first years of life

### 2022-04-29 code/analysis.Rmd
Add descriptive stats for the Introduction

# Read sheets
screening <- readxl::read_excel(excel_file, sheet = "screening")
included <- readxl::read_excel(excel_file, sheet = "included", na = "NA")
```

```{r, prepare_effect_sizes}
# Add columns to the table of included experiments
included %>%
  mutate(

@@

>>>>

# Read sheets
screening <- readxl::read_excel(excel_file, sheet = "screening")
included <- readxl::read_excel(excel_file, sheet = "included", na = "NA")

# Add columns to the table of included experiments
included %>%
  mutate(

@@

# Introduction

```{r, results_literature_search}
# Number of experiments
nrow(dat)

# Number of infants
sum(dat$sample_size)

# Age range in months
min(dat$age_min, na.rm = TRUE) / 30.417
max(dat$age_max, na.rm = TRUE) / 30.417

# Mean age in months
sum((dat$age_mean * dat$sample_size)) / sum(dat$sample_size) / 30.417

# Number of experiments per task type
table(dat$task)
```
